Long groovy title goes here

### 2013-06-22 shanghai.tex
Some fixes to proof of local constancy in pullback

\begin{proof}
Let $\cs{L}$ be a character sheaf on $G$. We start by showing that ${\bar f}^*\gcs{L}$ is locally constant on connected components of ${\bar H}$. Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any connected component. Then there is a unique connected component $c_i : {\bar G}^i$ of ${\bar G}$ such that ${\bar f}: {\bar H} \to {\bar G}$ factors through ${\bar H}^j \hookrightarrow {\bar G}^i$, thus defining ${\bar f}^j : {\bar H}^j \to {\bar G}^i$. Indeed, $i$ is the image of $j$ under the group homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.\Clifton{Replace with a better reference, eventually.} Since $\cs{L}$ is a character sheaf, $\gcs{L}$ is locally constant on the connect components of ${\bar G}$; thus, there is a finite etale covering $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G}^i)$ is constant. Let $b_j : Y_j \to {\bar H}^j$ be the pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be the map opposite ${\bar f}^j$. Then $b_j$ is a finite etale covering of ${\bar H}^j$ and 
\[
b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right) = ({\bar f}\circ c_j \circ b_j)^*\gcs{L} = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G}^i).
\]
Since $a_i^* (\gcs{L}\vert_{\bar G}^i)$ is a constant sheaf and since the pull-back of a constant sheaf (along $g_j$, in this case) is a constant sheaf, it follows that $b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)$ is a constant sheaf. Thus, ${\bar f}^*\gcs{L}$ is locally constant on ${\bar H}^j$. Since $({\bar f}^*\gcs{L})_{\bar g} = \gcs{L}_{f({\bar g})}$ for every geometric point ${\bar g}$ on ${\bar G}$, and since $\gcs{L}$ has rank $1$ on connected components of ${\bar G}$, it follows that $f^*\gcs{L}$ also has rank $1$ on connected components of ${\bar G}$. This completes the proof that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.0}.

>>>>

\begin{proof}
Let $\cs{L}$ be a character sheaf on $G$. We start by showing that ${\bar f}^*\gcs{L}$ is locally constant on connected components of ${\bar H}$. Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any connected component and let $i$ be the image of $j$ under the group homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.\Clifton{Replace with a better reference, eventually.}  Write $c_i : \bar{G}^i \hookrightarrow \bar{G}$ for the inclusion of $\bar{G}^i$ and ${\bar f}^j : {\bar H}^j \to {\bar G}^i$ for the restriction of $f$ to $\bar{H}^j$.  Since $\cs{L}$ is a character sheaf, $\gcs{L}$ is locally constant on the connect components of ${\bar G}$; thus, there is a finite etale covering $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G^i})$ is constant. Let $b_j : Y_j \to {\bar H}^j$ be the pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be the map opposite ${\bar f}^j$. Then $b_j$ is a finite etale covering of ${\bar H}^j$ and 
\[
b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right) = ({\bar f}\circ c_j \circ b_j)^*\gcs{L} = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G^i}).
\]
Since $a_i^* (\gcs{L}\vert_{\bar G^i})$ is a constant sheaf and since the pull-back of a constant sheaf (along $g_j$, in this case) is a constant sheaf, it follows that $b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)$ is a constant sheaf. Thus, ${\bar f}^*\gcs{L}$ is locally constant on ${\bar H}^j$. Since $({\bar f}^*\gcs{L})_{\bar g} = \gcs{L}_{f({\bar g})}$ for every geometric point ${\bar g}$ on ${\bar G}$, and since $\gcs{L}$ has rank $1$ on connected components of ${\bar G}$, it follows that $f^*\gcs{L}$ also has rank $1$ on connected components of ${\bar G}$. This completes the proof that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.0}.
